### 2013-05-08 doc/icml2013/evaluation.tex
Minor changes + experiments
Various fixes to make it submittable
experiments

\section{Empirical Evaluation}
\label{sec:evaluation}

\subsection{Experimental Setup}

@@

We solved the low rank recovery optimization routines for $M_2$ and
$M_3$ using \texttt{cvx}\citationneeded. 
%ainterior point method an interior proximal subgradient descent
%algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
%The algorithm was initialized with the regularized least squares
%solution and was run for 500 iterations or until convergence up to
%a tolerance of $10^{-3}$.
%Both regularization parameters, $\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$. 
As a baseline, we also implemented EM with two different
initializations. In the first, we used $\beta$s with random standard
Gaussian entries and uniform mixture probabilities, $\pi$. In the other,
we initialized EM with the starting points given by Spectral Experts.

\paragraph{Datasets}

We generated synthetic data as follows:
First, we generated a vector $t$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$.
Then, to get the actual covariates $x$, we applied a non-linear function of $t$
that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}.
The coefficients $\{\beta_h\}$ were drawn from a standard Gaussian. The
results presented below use $\sigma^2 = 0.1$; we did not observe any
qualitatively different behaviour for choices of $\sigma^2$ in the range
$[0.01, 0.4]$.

As an example, one feature map we considered in the one-dimensional
setting was $x = (1, t, t^4, t^7)$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using Spectral Experts are shown in
\figureref{fig:curves}. We note that even on well-separated data such as
this, EM converged to the correct basin of attraction only 13\% of the time.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.pdf}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, n = 500,000$}
  \label{fig:hist}
\end{figure}

\begin{figure*}[p]
  \centering
  \subfigure[Spectral, Spectral+EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{Visualization of the parameters estimated by Spectral Experts versus EM.
  (a) The dashed lines denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to further improve the solution (solid lines).
  (b) The dotted lines show different local optima found by EM.}
  \label{fig:curves}
\end{figure*}

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
%$\{1$, $ x_1$, $ x_1^4\}$ 
  1 & 4 & 2 & 1.52 $\pm$ 0.71 & 0.28 $\pm$ 0.82 & {\bf 0.13 $\pm$ 0.55} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
  2 & 5 & 2 & 2.92 $\pm$ 1.10 & 0.00 $\pm$ 0.00 & {\bf 0.00 $\pm$ 0.00} \\
  2 & 5 & 3 & 3.76 $\pm$ 1.93 & 0.43 $\pm$ 1.07 & {\bf 0.23 $\pm$ 0.76} \\
%$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  2 & 6 & 2 & 4.52 $\pm$ 1.67 & 0.63 $\pm$ 1.29 & {\bf 0.18 $\pm$ 0.66} \\
\belowspace
  2 & 6 & 5 & 6.78 $\pm$ 2.18 & 2.29 $\pm$ 1.79 & {\bf 1.77 $\pm$ 1.89} \\

@@

\begin{figure*}[tbhp]
  \centering
  \subfigure[Well-specified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Learning curves: parameter error as a function of the number of samples $n$ ($b = 1, d = 5, k = 3$).}
  \label{fig:vs-n}
\end{figure*}

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  2.94 $\pm$ 1.52 & 0.29 $\pm$ 0.85 &  {\bf 0.22 $\pm$ 0.72} \\
\belowspace
 2 & 5 & 3 &  3.82 $\pm$ 2.00 & 0.44 $\pm$ 1.12 &  {\bf 0.35 $\pm$ 1.00} \\
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline

>>>>

\section{Empirical evaluation}
\label{sec:evaluation}

In the previous section, we showed that Spectral Experts provides a consistent
estimator.  %that converges a $\frac{1}{\sqrt n}$
In this section, we explore the empirical properties of our algorithm on simulated data.
Our main finding is that Spectral Experts alone attains higher parameter error than EM,
but this is not the complete story.
If we initialize EM with the estimates returned by Spectral Experts,
then we end up with much better estimates than EM from a random initialization.
%In this section, we will support these theoretical results with
%experiments on simulated data.
%We will see that in the finite sample
%regime, even when Spectral Experts does not converge to the optimal
%answer, it provides robust initialization for local methods like EM.

\subsection{Experimental setup}

@@

We experimented with three algorithms.
The first algorithm (Spectral) is simply the Spectral Experts.
We set the regularization strengths $\lambda_n^{(2)} = \frac{1}{10^{5} \sqrt{n}}$
and $\lambda_n^{(3)} = \frac{1}{10^{3} \sqrt{n}}$;
the algorithm was not very sensitive to these choices.
We solved the low-rank regression to estimate $M_2$ and
$M_3$ using an off-the-shelf convex optimizer, CVX~\cite{cvx}.
%ainterior point method an interior proximal subgradient descent
%algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
%The algorithm was initialized with the regularized least squares
%solution and was run for 500 iterations or until convergence up to
%a tolerance of $10^{-3}$.
%Both regularization parameters, $\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$. 
The second algorithm (EM) is EM where the $\beta$'s are initialized from a standard normal
and $\pi$ was set to the uniform distribution plus some small perturbations.
We ran EM for 1000 iterations.
In the final algorithm (Spectral+EM),
we initialized EM with the output of Spectral Experts.

\paragraph{Data}

We generated synthetic data as follows:
First, we generated a vector $t$ sampled uniformly over the $b$-dimensional
unit hypercube $[-1,1]^b$.
Then, to get the actual covariates $x$, we applied a non-linear function of $t$
that conformed to the identifiability criteria discussed in
\sectionref{sec:algo}.
The true regression coefficients $\{\beta_h\}$ were drawn from a standard normal
and $\pi$ is set to the uniform distribution.
The observation noise $\epsilon$ is drawn from a normal with variance $\sigma^2$.
Results are presented below for $\sigma^2 = 0.1$, but we did not observe any
qualitatively different behaviour for choices of $\sigma^2$ in the range
$[0.01, 0.4]$.

As an example, one feature map we considered in the one-dimensional
setting $(b=1)$ was $x = (1, t, t^4, t^7)$. The data and the curves fit using
Spectral Experts, EM with random initializations and EM initialized with
the parameters recovered using Spectral Experts are shown in
\figureref{fig:curves}. We note that even on well-separated data such as
this, EM converged to the correct basin of attraction only 13\% of the time.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.50\textwidth]{figures/hist.png}
  \caption{Histogram over recovery errors between the three algorithms. $b = 1, d = 4, k = 3, n = 500,000$}
  \label{fig:hist}
\end{figure}

\begin{figure*}[p]
  \centering
  \subfigure[Spectral, Spectral+EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.png}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.png}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{Visualization of the parameters estimated by Spectral Experts versus EM.
  (a) The dashed lines denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to further improve the solution (solid lines).
  (b) The dotted lines show different local optima found by EM.}
  \label{fig:curves}
\end{figure*}

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
%$\{1$, $ x_1$, $ x_1^4\}$ 
  1 & 4 & 2 & 2.45 $\pm$ 3.68 & 0.28 $\pm$ 0.82 & {\bf 0.17 $\pm$ 0.57} \\
% 1-5-2 2.451423 (+/- 3.686348) 0.176685 (+/- 0.579108) 0.007634 (+/- 0.001706) 0.341620 (+/- 0.584178) 0.010296 (+/- 0.007839)
%$\{1$, $ x_1$, $ x_2$, $ x_1^2 x_2^2\}$ 
2 & 5 & 2 & 1.38 $\pm$ 0.84 & {\bf 0.00 $\pm$ 0.00} & {\bf 0.00 $\pm$ 0.00} \\
% 2-3-2 1.383626 (+/- 0.840325) 0.001416 (+/- 0.000083) 0.003312 (+/- 0.000399) 0.454076 (+/- 0.758689) 0.003340 (+/- 0.000397)
  2 & 5 & 3 & 2.92 $\pm$ 1.71 & 0.43 $\pm$ 1.07 & {\bf 0.31 $\pm$ 1.02} \\
% 2-3-3 2.917581 (+/- 1.714054) 0.308649 (+/- 1.024135) 0.003885 (+/- 0.000442) 0.661009 (+/- 0.543162) 0.012455 (+/- 0.033185)
%$\{1$, $ x_1$, $ x_2$, $ x_1 x_2^3$, $ x_1^2 x_2^2$, $ x_1^3 x_2 \}$ 
  2 & 6 & 2 & 2.33 $\pm$ 0.67 & 0.63 $\pm$ 1.29 & {\bf 0.01 $\pm$ 0.01} \\
% 2-4-2 2.333000 (+/- 0.674578) 0.004067 (+/- 0.001391) 0.001167 (+/- 0.001096) 0.592667 (+/- 0.478518) 0.001200 (+/- 0.001143)
%\belowspace
%  2 & 6 & 5 & 6.78 $\pm$ 2.18 & 2.29 $\pm$ 1.79 & {\bf 1.77 $\pm$ 1.89} \\

@@

\begin{figure*}[tbhp]
  \centering
  \subfigure[Well-specified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.png}
  }
    \hspace{-2em}
  \subfigure[Misspecified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.png}
  }
  \caption{Learning curves: parameter error as a function of the number of samples $n$ ($b = 1, d = 5, k = 3$).}
  \label{fig:vs-n}
\end{figure*}

@@

  \begin{tabular}{ r r r c c c }
\hline
\abovespace\belowspace
Variables ($b$) & Features ($d$) & Components ($k$) & Spectral & EM & Spectral + EM \\
\hline
\abovespace
 1 & 4 & 2 &  1.55 $\pm$ 0.84 & 0.29 $\pm$ 0.85 &  {\bf 0.01 $\pm$ 0.07} \\
 % 1-5-2 1.553269 (+/- 0.841002) 0.008463 (+/- 0.067282) 0.006283 (+/- 0.007291) 0.700833 (+/- 1.650770) 0.006344 (+/- 0.007351) 0.124876 (+/- 0.145539) 2.304894 (+/- 2.457321)
%\belowspace
 2 & 5 & 3 &  1.37 $\pm$ 0.85 & 0.44 $\pm$ 1.12 &  {\bf 0.00 $\pm$ 0.00} \\
% 2-3-2 1.373689 (+/- 0.849721) 0.002074 (+/- 0.000116) 0.004720 (+/- 0.000000) 0.501348 (+/- 0.656840) 0.004702 (+/- 0.000009)
 2 & 6 & 5 &  9.89 $\pm$ 4.46 & {\bf 2.53 $\pm$ 1.77} &  2.69 $\pm$ 1.83 \\
 2 & 8 & 7 & 23.07 $\pm$ 7.10 & 9.62 $\pm$ 1.03 &  {\bf 8.16 $\pm$ 2.31}  \\
\hline

### 2013-05-08 doc/icml2013/theory.tex
experiments

\begin{theorem}[Convergence of Spectral Experts]
\label{thm:convergence}
Assume each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d.\ points independently drawn from a mixture
of linear regressions model with parameter $\theta^*$.\footnote{Having three independent copies simplifies the analysis.}
Further, assume 
$\|x\|_2 \le R$, 
$\|\beta_h^*\|_2 \le L$ for all $h \in [k]$,
$|\epsilon| \le S$
and $B$ is rank $k$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Let $\epsilon$ be such that, 
$$\epsilon = O\left( \min\left\{ \frac{k\|M_3\|_\op \pi_{\max}}{\sigma_k(M_2)^{3/2}}, \half \right\}\right).$$ 
Suppose the number of samples is
$n = \max(n_1,n_2)$
where 
\begin{align*}
n_1 &= \Omega \left(\frac{R^{12} \log(1/\delta)}{\min_{p \in [3]} \sigmamin(\Sigma_p)^2} \right) \\
n_2 &= \Omega \left(\epsilon^{-2}~ \frac{k^2 \pi^2_{\max} \|M_3\|_\op^2}{\sigma_k(M_2)^{5} }\frac{ L^{6} S^{6} R^{12}}{\sigmamin(\Sigma_1)^2} \log(1/\delta) \right).
\end{align*}
If each regularization strength $\lambda_n^{(p)}$ is set to 
$$\Theta\left( L^p S^p R^{2p} \sqrt{\frac{\log(1/\delta)}{n}} \right),$$
for $p \in 2, 3$,
%$O\left(\frac{\sigmamin(\Sigma_p)}{\sqrt{k}}~ \epsilon \right)$, 
%$\Omega\left(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}}\right)$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriately permuted)
satisfies 
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} \le \epsilon \quad\quad 
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 \le \epsilon
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}}~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
%$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
%and for all $h \in [k]$,
%$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\sqrt{\pi_h^*}}$.
\end{theorem}

@@

\begin{lemma}[upper bound on adjoint operator]
\label{lem:lowRankUpper}
% Let $\opX_p$ be the linear operator previously defined. 
If $$n = \Omega \left(\max_{p\in [3]} \frac{L^{2p} S^{2p} R^{4p} \log(1/\delta)}{ \sigmamin(\Sigma_1)^2 \left(\lambda_n^{(p)}\right)^2} \right),$$
then with probability at least $1-\delta$:
$$\lambda_n^{(p)} \ge \frac1{n} \|\opX_p^*(\eta_p)\|_\op,$$
for each $p \in [3]$.
\end{lemma}

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower} Let $\|\hat M_2 - M_2\|_\op \le \epsilon$ and
  $\|\hat M_3 - M_3\|_\op \le \epsilon$, for some $\epsilon$ in
  $$O\left( \min\left\{ 
    \frac{\sigma_k(M_2)}{2}, 
    \frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_3\|_\op} 
    \right\}\right).$$ 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty}
  &= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2
  &= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}

@@

\begin{proof}[Proof of Theorem 1]
By \reflem{lowRank}, \reflem{lowRankLower} and \reflem{lowRankUpper}, we
can control the Frobenius norm of the error in the moments, which
directly upper bounds the operator norm: If $n \ge \max\{n_1, n_2\}$,
then
\begin{align}
  \|\hat M_p - M_p\|_\op = O\left( \lambda_n^{(p)} \sqrt{k} \sigmamin(\Sigma_p)^{-1} \right).
  %\|\hat M_p - M_p\|_\op = O\left( \sigma^3 L^3 R^6 k^{\frac12} \sigmamin(\Sigma_p)^{-1} \sqrt{\frac{\log^3 (1/\delta)}{n}} \right).
  %\|\hat M_p - M_p\|_F = O\left( \frac{\sigma^3 L^3 R^6 \sqrt{k} \log^3 (1/\delta)}{\sqrt{n} (\sigmamin(\Sigma_p) - d^p R^p \sqrt{\frac{p \log(d) \log(1/\delta)}{n}}} \right).
\end{align}

>>>>

\begin{theorem}[Convergence of Spectral Experts]
\label{thm:convergence}
Assume each dataset $\sD_p$ (for $p = 1, 2, 3$) consists of $n$ i.i.d.\ points independently drawn from a mixture
of linear regressions model with parameter $\theta^*$.\footnote{Having three independent copies simplifies the analysis.}
Further, assume 
$\|x\|_2 \le R$, 
$\|\beta_h^*\|_2 \le L$ for all $h \in [k]$,
$|\epsilon| \le S$
and $B$ is rank $k$.
Let $\Sigma_p \eqdef \E[\cvec(x\tp{p})\tp{2}]$, 
and assume $\Sigma_p \succ 0$ for each $p \in \{1,2,3\}$.
Let $\epsilon$ be such that, 
$$\epsilon = O\left( \min\left\{ \frac{k\|M_3\|_\op \pi_{\max}}{\sigma_k(M_2)^{3/2}}, \half \right\}\right).$$ 
Suppose the number of samples is
$n = \max(n_1,n_2)$
where 
\begin{align*}
n_1 &= \Omega \left(\frac{R^{12} \log(1/\delta)}{\min_{p \in [3]} \sigmamin(\Sigma_p)^2} \right) \\
n_2 &= \Omega \left(\epsilon^{-2}~ \frac{k^2 \pi^2_{\max} \|M_3\|_\op^2}{\sigma_k(M_2)^{5}} L^{6} S^{6} R^{12} \log(1/\delta) \right).
\end{align*}
If each regularization strength $\lambda_n^{(p)}$ is set to 
$$\Theta\left( L^p S^p R^{2p} \sqrt{\frac{\log(1/\delta)}{n}} \right),$$
for $p \in 2, 3$,
%$O\left(\frac{\sigmamin(\Sigma_p)}{\sqrt{k}}~ \epsilon \right)$, 
%$\Omega\left(\sigma^3 L^3 R^6 \sqrt{\frac{\log(1/\delta)}{n}}\right)$,
then the parameter estimates $\hat\theta = (\hat\pi, \hat B)$ returned by
\algorithmref{algo:spectral-experts} (with the columns appropriately permuted)
satisfies 
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty} \le \epsilon \quad\quad 
  %&= O\left(\frac{k \pi_{\max}^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2 \le \epsilon
  %&= O\left( \frac{k \pi_{\max} \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}}~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
%$\|\hat\pi - \pi^*\|_{\infty} \le \epsilon$
%and for all $h \in [k]$,
%$\|\hat\beta_h - \beta^*_h\|_2 \le \frac{\epsilon}{\sqrt{\pi_h^*}}$.
\end{theorem}

@@

\begin{lemma}[upper bound on adjoint operator]
\label{lem:lowRankUpper}
% Let $\opX_p$ be the linear operator previously defined. 
If $$n = \Omega \left(\max_{p\in [3]} \frac{L^{2p} S^{2p} R^{4p} \log(1/\delta)}{\left(\lambda_n^{(p)}\right)^2} \right),$$
then with probability at least $1-\delta$:
$$\lambda_n^{(p)} \ge \frac1{n} \|\opX_p^*(\eta_p)\|_\op,$$
for each $p \in [3]$.
\end{lemma}

@@

Having bounded the error of the compound parameter estimates $\hat M_2$ and $\hat M_3$,
we will now study how this error propagates through the tensor factorization step of 
\algorithmref{algo:spectral-experts},
which includes whitening, applying the robust tensor power method \cite{AnandkumarGeHsu2012},
and unwhitening.
\begin{lemma}
  \label{lem:tensorPower} Let $\|\hat M_2 - M_2\|_\op \le \epsilon$ and
  $\|\hat M_3 - M_3\|_\op \le \epsilon$, for some $\epsilon$ in
  $$O\left( \min\left\{ 
    \frac{\sigma_k(M_2)}{2}, 
    \frac{\sigma_k(M_2)^{5/2}}{k \pi_{\max} \|M_3\|_\op} 
    \right\}\right).$$ 
  Then, there exists a permutation of indices such that  the parameter
  estimates found in step 2 of \algorithmref{algo:spectral-experts}
  satisfy the following with probability at least $1 - \delta$:
  \begin{align*}
  \|\hat \pi - \pi \|_{\infty}
  &= O\left(\frac{k \pi_1^{5/2}\| {M_3} \|_\op}{\sigma_k(M_2)^{5/2}} ~ \epsilon \right) \\
  \|\hat \beta_h - \beta_h\|_2
  &= O\left( \frac{k \pi_1 \|M_2\|_\op^{1/2} \| {M_3} \|_\op}{ \sigma_k(M_2)^{5/2} }~ \epsilon \right),
  \end{align*}
  for all $h \in [k]$.
\end{lemma}

@@

\begin{proof}[Proof of Theorem 1 (sketch)]
By \reflem{lowRank}, \reflem{lowRankLower} and \reflem{lowRankUpper}, we
can control the Frobenius norm of the error in the moments, which
directly upper bounds the operator norm: If $n \ge \max\{n_1, n_2\}$,
then
\begin{align}
  \|\hat M_p - M_p\|_\op = O\left( \lambda_n^{(p)} \sqrt{k} \sigmamin(\Sigma_p)^{-1} \right).
  %\|\hat M_p - M_p\|_\op = O\left( \sigma^3 L^3 R^6 k^{\frac12} \sigmamin(\Sigma_p)^{-1} \sqrt{\frac{\log^3 (1/\delta)}{n}} \right).
  %\|\hat M_p - M_p\|_F = O\left( \frac{\sigma^3 L^3 R^6 \sqrt{k} \log^3 (1/\delta)}{\sqrt{n} (\sigmamin(\Sigma_p) - d^p R^p \sqrt{\frac{p \log(d) \log(1/\delta)}{n}}} \right).
\end{align}
